Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/conclusions.tex
massive spellchecking

Ultrafast Electron Microscopy is an exciting new field of intrumentation research which promises to open our eyes to the dynamics occurring in nanoscale processes.

@@

In this thesis I have presented the extended Analytic Gaussian (AG) model, an effiecient numerical model based on the work of Michalik and Sipe~\cite{michalik_analytic_2006}, but extended so as to be useful in modeling the dynamics of ultrafast electron pulses in microscope columns.
For pulses containing $N$ carriers of charge $e$ and mass $m$, the model is simply these four equations,
\begin{subequations}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi) + \sigma_{\alpha} \sum\limits_{f} M_{\alpha}^{\lbrace f \rbrace} \label{eq:ag_model_gamma_conc} \,\text{.}
\end{gather}
\end{subequations}
where the subscript $\alpha$ denotes the directionality of the dynamics, either $\smallT$ for the transverse or $z$ for the longitudinal.
At any time $t$, the $\sigma_{\alpha}$ quantities characterize the spatial variance of the pulse and $\gamma_{\alpha}$ represent the momentum chirp across the pulse.
A third parameter, the local momentum variance $\eta_{\alpha}$, is also encoded in these equations.
By Liouville's theorem, which the AG model explicitly satisfies, we know that the product of the spatial variance $\sigma_{\alpha}$ and the local momentum variance $\eta_{\alpha}$ is constant throughout propagation (for perfect lensing and without clipping the puse), so we define the constant,
\begin{equation} \label{eq:define_big_gamma_conc}
  \Gamma_{\alpha}^2 \equiv \sigma_{\alpha} \eta_{\alpha} \,\text{.}
\end{equation}
By evaluating this constant once, presumably from initial conditions, and later applying \ref{eq:define_big_gamma_conc} we can get the extract these $\eta_{\alpha}$ parameters while only needing to compute the other four.
The parameter $\xi$ characterizes the ellipticity of the pulse,
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}} \,\text{,}
\end{equation}
and the family of $L$ functions (defined in \ref{eq:ag_l_family}) are smooth and well behaved functions for all physically meaningful $\xi$.
Finally the $M_{\alpha}^{\lbrace f \rbrace}$ quantities define the $\alpha$ diretion influence of the $f^{\text{th}}$ external force.

In UEM, the initial pulse conditions are of notable importance for the performance of the instrument.
Therefore I have presented a simplistic but useful set of initial conditions for the AG model.
First lets assume we photocathode which has a work function $\Phi$, the energy an electron must absorb before it is freed to leave the material.
Lets assume that the photocathode is in an acceleration region, having an applied electric field $E_{DC}$.
Finally, lets assume we have a laser pulse whose intensity $I$ is of the form,
\begin{equation}
  I ( x , y , t ) = I_{0} \exp \left ( - \frac{ ( x^{2} +y^{2} ) }{ w^{2} } - \frac{ t^{ 2 } }{ \tau^{ 2 } } \right ) \punct{,}
\end{equation}
where $w$ and $\tau$ are the HW1/eM laser pulse width and duration respectively, and the photon energy $\hbar \omega$ is greater than $\Phi$, thus permitting single-photon photoemission.
Ejected electrons will then carry an excess photoemission energy $\Delta E = \hbar \omega - \Phi$, so that the maximum velocity that an ejected electron may have is $ v_{max} = \sqrt{ 2 \Delta E / m } $.
Given these generic assumptions, the resulting initial conditions are simply,
\begin{subequations}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) \approx \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) \approx \frac{ ( v_{max} \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) \approx 0 \\
    \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{max} + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \\
    \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 ) }{ 4 } \punct{.}
  \end{gather}
\end{subequations}
In Section \ref{sec:bin_model} I have also presented a binning model which, when fully investigated, may eventually be employed rather than this simplisitc set of initial conditions.

@@

A common figure of merit for electron beams is its normalized transverse emittance~\cite{jensen_emittance_2010}, $\varepsilon_{\smallT}$, which for the usual case of axially symmetric electron pulses has the form,
\begin{equation}
  \varepsilon_{\smallT} = \frac{1}{m c} \Delta x \Delta p_{\smallT} \,\text{,}
\end{equation}
where $\Delta x$ and $\Delta p_{\smallT}$ are the transverse spatial uncertainty and transverse momentum uncertainty, respectively.
This quantity is conserved under propagation through free space and perfect electron-optical, though it may increase for imperfect ones~\cite{oshea_reversible_1998}.
The normalized transverse emittance limits the resolving capablility of the beam, so this quantity can be thought of as a measure of the beam quality, where a lower number is preferred~\cite{berger_dc_2009}.
Since we have already established that a large area emission source must be used, the only avenue to reduce $\varepsilon_{\smallT}$ is to reduce the transverse momentum uncertainty, which is dependent on the photocathode and photoemission process employed.

>>>>

Ultrafast Electron Microscopy is an exciting new field of instrumentation research which promises to open our eyes to the dynamics occurring in nanoscale processes.

@@

In this thesis I have presented the extended Analytic Gaussian (AG) model, an efficient numerical model based on the work of Michalik and Sipe~\cite{michalik_analytic_2006}, but extended so as to be useful in modeling the dynamics of ultrafast electron pulses in microscope columns.
For pulses containing $N$ carriers of charge $e$ and mass $m$, the model is simply these four equations,
\begin{subequations}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{ \Gamma_{\alpha}^2 + \gamma_{\alpha}^2 }{\sigma_{\alpha} m}
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi) + \sigma_{\alpha} \sum\limits_{f} M_{\alpha}^{\lbrace f \rbrace} \label{eq:ag_model_gamma_conc} \,\text{.}
\end{gather}
\end{subequations}
where the subscript $\alpha$ denotes the directionality of the dynamics, either $\smallT$ for the transverse or $z$ for the longitudinal.
At any time $t$, the $\sigma_{\alpha}$ quantities characterize the spatial variance of the pulse and $\gamma_{\alpha}$ represent the momentum chirp across the pulse.
A third parameter, the local momentum variance $\eta_{\alpha}$, is also encoded in these equations.
By Liouville's theorem, which the AG model explicitly satisfies, we know that the product of the spatial variance $\sigma_{\alpha}$ and the local momentum variance $\eta_{\alpha}$ is constant throughout propagation (for perfect lensing and without clipping the pulse), so we define the constant,
\begin{equation} \label{eq:define_big_gamma_conc}
  \Gamma_{\alpha}^2 \equiv \sigma_{\alpha} \eta_{\alpha} \,\text{.}
\end{equation}
By evaluating this constant once, presumably from initial conditions, and later applying \ref{eq:define_big_gamma_conc} we can get the extract these $\eta_{\alpha}$ parameters while only needing to compute the other four.
The parameter $\xi$ characterizes the ellipticity of the pulse,
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}} \,\text{,}
\end{equation}
and the family of $L$ functions (defined in \ref{eq:ag_l_family}) are smooth and well behaved functions for all physically meaningful $\xi$.
Finally the $M_{\alpha}^{\lbrace f \rbrace}$ quantities define the $\alpha$ direction influence of the $f^{\text{th}}$ external force.

In UEM, the initial pulse conditions are of notable importance for the performance of the instrument.
Therefore I have presented a simplistic but useful set of initial conditions for the AG model.
First lets assume we photocathode which has a work function $\Phi$, the energy an electron must absorb before it is freed to leave the material.
Lets assume that the photocathode is in an acceleration region, having an applied electric field $E_{DC}$.
Finally, lets assume we have a laser pulse whose intensity $I$ is of the form,
\begin{equation}
  I ( x , y , t ) = I_{0} \exp \left ( - \frac{ ( x^{2} +y^{2} ) }{ w^{2} } - \frac{ t^{ 2 } }{ \tau^{ 2 } } \right ) \punct{,}
\end{equation}
where $w$ and $\tau$ are the HW1/eM laser pulse width and duration respectively, and the photon energy $\hbar \omega$ is greater than $\Phi$, thus permitting single-photon photoemission.
Ejected electrons will then carry an excess photoemission energy $\Delta E = \hbar \omega - \Phi$, so that the maximum velocity that an ejected electron may have is $ v_{max} = \sqrt{ 2 \Delta E / m } $.
Given these generic assumptions, the resulting initial conditions are simply,
\begin{subequations}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) \approx \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) \approx \frac{ ( v_{max} \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) \approx 0 \\
    \gamma_{ z } ( 0 ) \approx \sqrt{ \sigma_{ z } ( 0 ) } \left ( m v_{max} + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \\
    \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 ) }{ 4 } \punct{.}
  \end{gather}
\end{subequations}
In Section \ref{sec:bin_model} I have also presented a binning model which, when fully investigated, may eventually be employed rather than this simplistic set of initial conditions.

@@

A common figure of merit for electron beams is its normalized transverse emittance~\cite{jensen_emittance_2010}, $\varepsilon_{\smallT}$, which for the usual case of axially symmetric electron pulses has the form,
\begin{equation}
  \varepsilon_{\smallT} = \frac{1}{m c} \Delta x \Delta p_{\smallT} \,\text{,}
\end{equation}
where $\Delta x$ and $\Delta p_{\smallT}$ are the transverse spatial uncertainty and transverse momentum uncertainty, respectively.
This quantity is conserved under propagation through free space and perfect electron-optical, though it may increase for imperfect ones~\cite{oshea_reversible_1998}.
The normalized transverse emittance limits the resolving capability of the beam, so this quantity can be thought of as a measure of the beam quality, where a lower number is preferred~\cite{berger_dc_2009}.
Since we have already established that a large area emission source must be used, the only avenue to reduce $\varepsilon_{\smallT}$ is to reduce the transverse momentum uncertainty, which is dependent on the photocathode and photoemission process employed.

### 2013-04-12 inc/design_considerations/considerations.tex
massive spellchecking

It is straightforward to show that in order to make a useful image in an electron microcope, the number of electrons collected must be above some minimum number.
The Rose criterion~\cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k $\times$ 1k CCD camera, this implies an incident electron pulse with $N=10^8$~\cite{armstrong_prospects_2007}.

In a conventional electron microscope the electrons are generated by one of several processes, often by heating the cathode or applying a large field to the cathode, or combinations thereof.
Although these processes produce a very large number of electrons, far more than required by the Rose criterion, they are essentially not highly directional.
A pinhole is used to eliminate most of the electrons, with the exception of those which will travel down the column axis, thereby reducing the beam current but producing a high-quality beam.
%TODO ref(s)
For conventional electron microscopes without time resolution, the Rose criterion may be met for arbitrarily low beam current by simply allowing the image to acquire for a long enough time to collect sufficent electrons.
Further, high beam current may be damaging to the sample over time, so a lower beam current is often preferred.

@@

This steady-state law for the maximum current density that can be achieved is not valid in the regime of interest for UEM (and UED) where the use of picosecond and femtosecond photocathode drive laser pulses implies that $t_{gun}$ is usually much greater than the electron pulse duration $\tau_e$.
Though there is no clear delineation in the literature or the community between moniker of Ultrafast Electron Microscopy (UEM) and the more general term Dynamic Transmission Electron Microcopy (DTEM), we propose that this is useful delimination, reserving the term UEM for those systems where the pulse can be completely contained inside the accelerator, i.e. $t_{gun} > \tau_e$.
Pulses of this type are subject to a different ``short pulse analog'' of the Child-Langmuir limit.

@@

This finally leads to the first consideration for UEM design mentioned in the introduction: for the clean pulsed emission of sufficient to create a useful image, the generated beam should have a HW1/eM width 
\begin{equation} \label{eq:minimum_w}
  w \gtrsim \sqrt{\frac{N e d}{\pi \varepsilon_0 V_{DC}}} \,\text{.}
\end{equation}
For our example case above, to cleanly extract $N \ge 10^8$ electrons/pulse we require $w \gtrsim 0.56 \text{ mm}$.
The effect that accomodating a large transverse pulse size has on designing an Ultrafast Electron Microscope will be discussed in Chapter \ref{chap:prototype}.

@@

This normalized transverse emittance limits the resolving capablility of the beam, so this quantity can be thought of as a measure of the beam quality, where a lower number is preferred~\cite{berger_dc_2009}.
Since \ref{eq:minimum_w} specifies a lower bound on the emission spot size $w$, knowing a UEM will exhibit higher resolution by employing an electron source with the minimum possible transverse emittance directly implies that every effort must be made to reduce the initial transverse momentum spread.
Though deriving an absolute limit on the allowable transverse emittance for imaging in a UEM would depend on many column-specific factors, since diffraction is expected to impose less stringent requirements on the beam than imaging, we may consider it when searching for an upper bound on transverse emittance.

>>>>

It is straightforward to show that in order to make a useful image in an electron microscope, the number of electrons collected must be above some minimum number.
The Rose criterion~\cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k $\times$ 1k CCD camera, this implies an incident electron pulse with $N=10^8$~\cite{armstrong_prospects_2007}.

In a conventional electron microscope the electrons are generated by one of several processes, often by heating the cathode or applying a large field to the cathode, or combinations thereof.
Although these processes produce a very large number of electrons, far more than required by the Rose criterion, they are essentially not highly directional.
A pinhole is used to eliminate most of the electrons, with the exception of those which will travel down the column axis, thereby reducing the beam current but producing a high-quality beam.
%TODO ref(s)
For conventional electron microscopes without time resolution, the Rose criterion may be met for arbitrarily low beam current by simply allowing the image to acquire for a long enough time to collect sufficient electrons.
Further, high beam current may be damaging to the sample over time, so a lower beam current is often preferred.

@@

This steady-state law for the maximum current density that can be achieved is not valid in the regime of interest for UEM (and UED) where the use of picosecond and femtosecond photocathode drive laser pulses implies that $t_{gun}$ is usually much greater than the electron pulse duration $\tau_e$.
Though there is no clear delineation in the literature or the community between moniker of Ultrafast Electron Microscopy (UEM) and the more general term Dynamic Transmission Electron Microscopy (DTEM), we propose that this is useful delimitation, reserving the term UEM for those systems where the pulse can be completely contained inside the accelerator, i.e. $t_{gun} > \tau_e$.
Pulses of this type are subject to a different ``short pulse analog'' of the Child-Langmuir limit.

@@

This finally leads to the first consideration for UEM design mentioned in the introduction: for the clean pulsed emission of sufficient to create a useful image, the generated beam should have a HW1/eM width 
\begin{equation} \label{eq:minimum_w}
  w \gtrsim \sqrt{\frac{N e d}{\pi \varepsilon_0 V_{DC}}} \,\text{.}
\end{equation}
For our example case above, to cleanly extract $N \ge 10^8$ electrons/pulse we require $w \gtrsim 0.56 \text{ mm}$.
The effect that accommodating a large transverse pulse size has on designing an Ultrafast Electron Microscope will be discussed in Chapter \ref{chap:prototype}.

@@

This normalized transverse emittance limits the resolving capability of the beam, so this quantity can be thought of as a measure of the beam quality, where a lower number is preferred~\cite{berger_dc_2009}.
Since \ref{eq:minimum_w} specifies a lower bound on the emission spot size $w$, knowing a UEM will exhibit higher resolution by employing an electron source with the minimum possible transverse emittance directly implies that every effort must be made to reduce the initial transverse momentum spread.
Though deriving an absolute limit on the allowable transverse emittance for imaging in a UEM would depend on many column-specific factors, since diffraction is expected to impose less stringent requirements on the beam than imaging, we may consider it when searching for an upper bound on transverse emittance.

### 2013-04-12 inc/extension/external_forces/formal.tex
as I have suspected, the only previous model I need to introduce is the AG model.
This commit changes the introductions of several chapters and lowers the headings by one in the new AG model chapter
massive spellchecking

Simulation of electron pulse propagation in UEM and modern UED apparatus~\cite{siwick_ultrafast_2002,oudheusden_electron_2007,reed_femtosecond_2006} requires the ability to model electron-optical elements designed to control the three-dimensional space-charge and dispersion induced broadening of the pulse, and hence deliver electron pulses of the desired quality to the specimen. 
The Analytic Gaussian model as presented by Michalik and Sipe (see Section \ref{sec:ms_model}) is only useful for modeling free-space propagation.
This is because there is no allowance for external forces, such as those imparted by the ``optical'' elements of an electron microscope column.
In this section, I show that the AG model can be extended to include external forces on the pulse, such as the influence of magnetic electron lenses and RF pulse compression cavities~\cite{oudheusden_electron_2007,veisz_hybrid_2007}.

@@

While the free-space AG model does not contain any external forces, it does include an internal force: the Coulomb force is included to model the repulsion of the pulse's electrons from each other.
As this force is self-influencing, it is the major souce of complexity in the model; indeed without this term, a complete analytic solutions is possible, which is identical to ``Gaussian'' optics~\cite{michalik_analytic_2006}.

@@

Since these terms are only added to $\dfrac{d \gamma_{\alpha}}{d t}$, the analysis of Liouville's Theorem, shown in Section \ref{sec:liouville}, is unaffected: the \textit{extended} AG model still explicitly satisfies Liouvilles's Theorem.

>>>>

Simulation of electron pulse propagation in UEM and modern UED apparatus~\cite{siwick_ultrafast_2002,oudheusden_electron_2007,reed_femtosecond_2006} requires the ability to model electron-optical elements designed to control the three-dimensional space-charge and dispersion induced broadening of the pulse, and hence deliver electron pulses of the desired quality to the specimen. 
The Analytic Gaussian model as presented by Michalik and Sipe (see Chapter \ref{chap:ms_model}) is only useful for modeling free-space propagation.
This is because there is no allowance for external forces, such as those imparted by the ``optical'' elements of an electron microscope column.
In this section, I show that the AG model can be extended to include external forces on the pulse, such as the influence of magnetic electron lenses and RF pulse compression cavities~\cite{oudheusden_electron_2007,veisz_hybrid_2007}.

@@

While the free-space AG model does not contain any external forces, it does include an internal force: the Coulomb force is included to model the repulsion of the pulse's electrons from each other.
As this force is self-influencing, it is the major source of complexity in the model; indeed without this term, a complete analytic solutions is possible, which is identical to ``Gaussian'' optics~\cite{michalik_analytic_2006}.

@@

Since these terms are only added to $\dfrac{d \gamma_{\alpha}}{d t}$, the analysis of Liouville's Theorem, shown in Section \ref{sec:liouville}, is unaffected: the \textit{extended} AG model still explicitly satisfies Liouville's Theorem.

### 2013-04-12 inc/extension/external_forces/practical.tex
massive spellchecking

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section, I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression~\cite{oudheusden_electron_2007} and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

The full description of the motion of an electron (in cylindrical coordinates $r, \theta, z$) in an azimuthally symmetric magnetic field ($\vec{B} = B_r \hat{r} + B_z \hat{z}$) is easily derived~\cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -e B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = e r \dot{r} B_z - e r B_r \dot{z} \\
  m \ddot{z} = e B_r r \dot{\theta} \,\text{,}
\end{gather}
\end{subequations}
where each dot denotes a time derivative.
Attempting to further seperate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
Compounding the problem, the full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell~\cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$, again in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  \frac{B_z}{\mu} = H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  \frac{B_r}{\mu} = H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q } \,\text{,}
\end{gather}
\end{subequations}
where $\mu$ is the local magnetic permability, $H$ is the auxiliary field, and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
In the vacuum, $\mu$ is simply the usual free space permeability $\mu_0$; in Section \ref{sec:mag_lens}, we will see how this permeability can be used to improve the performance of magnetic lenses.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

\begin{figure}
  \centering
  \input{mag_lens_plot}
  \caption[Comparison of the AG model and a kinematic model of a magnetic lens]{
    Comparison of electron rays tracked kinematically through a realistic magnetic lens simulation (green) and an AG model simulation of a Guassian electron beam (red) of a similar HW1/eM beam width $ w = 500 \mu\text{m} $.
  }
  \label{fig:mag_lens_loops}
\end{figure}

For localizing the region of influence of the lens, I have generally modelled a thin magnetic lens as having a super-Gaussian order value $n=1$, a simple Gaussian; of course this may depend on the specifics of the lens.
To simulate the effect of magnetic lenses in a UEM by the extended AG model, for each magnetic lens, one adds a term like
\begin{equation}
  M_{\smallT}^{mag} = M_{\smallT}^{mag}(I) \exp \left [ - \left (  \frac{ z^{\prime} - z_{mag}^{\prime} }{ L_{mag} / 2 } \right )^{ 2 } \right ] \text{,}
\end{equation}
to the set of $M_{\smallT}$ parameters, where $z_{mag}^{\prime}$ and $L_{mag}$ are the position and length of the lens in question respectively.

\ref{fig:mag_lens_loops} shows electron rays tracked kinematically (by employing \ref{eq:lens_eq_of_motion}) through a realistic magnetic lens simulation (shown in green).
The kinematic model employs ten individual current loops generating magnetic fields described by \ref{eq:field_of_loop}; these loops occupy a total length of 635$\mu$m at position $z=0$.
These loops each carry a current of 45A; this approximates a more realistic stack of 10 loops carrying 4.5A, thus simulating a  100 turn solenoid in a 10x10 array.
Each ray bunch consists of one ray parallel to the axis of propagation and one each having a longitudinal velocity of $1 \times 10^{8}$ m/s and an inward or outward transverse velocity related to an excess photoemission energy $\Delta E \approx $ 0.1eV.
The bunches are distributed evenly from $r=0$ to $r = 1$mm.
These are compared with an AG model simulation of a Guassian electron beam of HW1/eM beam width $ w = 500 \mu\text{m} $ having an initial transverse momentum variance associated with $\Delta E$.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $~\cite{kim_rf_1989}, where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs~\cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
As will be seen in Section \ref{sec:rf_cav_charge}, under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is generally smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $~\cite{kim_rf_1989}, even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

>>>>

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microscope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section, I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression~\cite{oudheusden_electron_2007} and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

The full description of the motion of an electron (in cylindrical coordinates $r, \theta, z$) in an azimuthally symmetric magnetic field ($\vec{B} = B_r \hat{r} + B_z \hat{z}$) is easily derived~\cite{el-kareh_electron_1970},
\begin{subequations} \label{eq:lens_eq_of_motion}
\begin{gather}
  m \ddot{r} = -e B_z r \dot{\theta} + m r \dot{\theta}^2                 \\
  \frac{d}{dt} ( m r^2 \dot{\theta} ) = e r \dot{r} B_z - e r B_r \dot{z} \\
  m \ddot{z} = e B_r r \dot{\theta} \,\text{,}
\end{gather}
\end{subequations}
where each dot denotes a time derivative.
Attempting to further separate these equations quickly highlights the tightly coupled nature of the motion of the electron in this system.
Compounding the problem, the full description of the off-axis field of a real (non-infinite) air-core solenoid is also surprisingly complicated.
Montgomery and Terrell~\cite{montgomery_some_1961} provide a full treatment for many lens configurations, including a tractable treatment for a single current loop of radius $a$, again in cylindrical coordinates, 
\begin{subequations} \label{eq:field_of_loop}
\begin{gather}
  \frac{B_z}{\mu} = H_z = \frac{2I}{\sqrt{Q}} \left(   F(k) + \frac{ a^2 - r^2 - z^2 }{ (1-k^2) Q } E(k) \right) \\
  \frac{B_r}{\mu} = H_r = \frac{2I}{\sqrt{Q}} \left( - F(k) + \frac{ a^2 + r^2 + z^2 }{ (1-k^2) Q } E(k) \right) \\
  Q \equiv (a+r)^2 + z^2 \\
  k \equiv \sqrt{ 4 a r / Q } \,\text{,}
\end{gather}
\end{subequations}
where $\mu$ is the local magnetic permeability, $H$ is the auxiliary field, and $F(k)$ and $E(k)$ are the complete elliptic integrals of the first and second kind respectively.
In the vacuum, $\mu$ is simply the usual free space permeability $\mu_0$; in Section \ref{sec:mag_lens}, we will see how this permeability can be used to improve the performance of magnetic lenses.
An even more accurate solenoid can be modeled by appropriately summing the fields of many such loops.

@@

\begin{figure}
  \centering
  \input{mag_lens_plot}
  \caption[Comparison of the AG model and a kinematic model of a magnetic lens]{
    Comparison of electron rays tracked kinematically through a realistic magnetic lens simulation (green) and an AG model simulation of a Gaussian electron beam (red) of a similar HW1/eM beam width $ w = 500 \mu\text{m} $.
  }
  \label{fig:mag_lens_loops}
\end{figure}

For localizing the region of influence of the lens, I have generally modeled a thin magnetic lens as having a super-Gaussian order value $n=1$, a simple Gaussian; of course this may depend on the specifics of the lens.
To simulate the effect of magnetic lenses in a UEM by the extended AG model, for each magnetic lens, one adds a term like
\begin{equation}
  M_{\smallT}^{mag} = M_{\smallT}^{mag}(I) \exp \left [ - \left (  \frac{ z^{\prime} - z_{mag}^{\prime} }{ L_{mag} / 2 } \right )^{ 2 } \right ] \text{,}
\end{equation}
to the set of $M_{\smallT}$ parameters, where $z_{mag}^{\prime}$ and $L_{mag}$ are the position and length of the lens in question respectively.

\ref{fig:mag_lens_loops} shows electron rays tracked kinematically (by employing \ref{eq:lens_eq_of_motion}) through a realistic magnetic lens simulation (shown in green).
The kinematic model employs ten individual current loops generating magnetic fields described by \ref{eq:field_of_loop}; these loops occupy a total length of 635$\mu$m at position $z=0$.
These loops each carry a current of 45A; this approximates a more realistic stack of 10 loops carrying 4.5A, thus simulating a  100 turn solenoid in a 10x10 array.
Each ray bunch consists of one ray parallel to the axis of propagation and one each having a longitudinal velocity of $1 \times 10^{8}$ m/s and an inward or outward transverse velocity related to an excess photoemission energy $\Delta E \approx $ 0.1eV.
The bunches are distributed evenly from $r=0$ to $r = 1$mm.
These are compared with an AG model simulation of a Gaussian electron beam of HW1/eM beam width $ w = 500 \mu\text{m} $ having an initial transverse momentum variance associated with $\Delta E$.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $~\cite{kim_rf_1989}, where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs~\cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
As will be seen in Section \ref{sec:rf_cav_charge}, under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocussing for the electron pulse and the magnetic contribution is generally smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $~\cite{kim_rf_1989}, even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.
